map_enclosure_sites

### 2023-12-19 smelt_2019_allseasons/Zoop 2019.Rmd
Adding biofowling analysis

```{r}
zoopdietlong = pivot_longer(zoopdiet, cols = c(Ostracod, Cyclopoid, Calanoid, Cladocera, Harpacticoid, Other, Amphipod, Diptera),
                            names_to = "Taxa", values_to= "count")

zoopnos = group_by(zoopdiet, datatype, Season, Location) %>%
  summarize(N = length(unique(SampleID)))

>>>>

```{r}
zoopdietlong = pivot_longer(zoopdiet, cols = c(Ostracod, Cyclopoid, Calanoid, Cladocera, Harpacticoid, Other, Amphipod, Diptera),
                            names_to = "Taxa", values_to= "count") %>%
  mutate(Location = case_when(Location == "DWSC" ~ "SDWSC",
                              Location == "RV" ~ "Rio Vista",
                              Location == "SM" ~ "Suisun Marsh",
                              Location == "YB" ~ "Yolo Bypass"))

zoopnos = group_by(zoopdiet, datatype, Season, Location) %>%
  summarize(N = length(unique(SampleID))) %>%
  mutate(Location = case_when(Location == "DWSC" ~ "SDWSC",
                              Location == "RV" ~ "Rio Vista",
                              Location == "SM" ~ "Suisun Marsh",
                              Location == "YB" ~ "Yolo Bypass"))

### 2023-12-19 smelt_2019_allseasons/map_enclosure_sites2019.Rmd
Adding biofowling analysis

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326)
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
```

>>>>

stations_sf <- st_as_sf(latlon, coords = c("Longitude", "Latitude"), crs = 4326) %>%
  mutate(Location = case_when(Location == "SRDWSC" ~ "SDWSC",
                              TRUE ~ Location))
data("us_states", package = "spData")
California = dplyr::filter(us_states, NAME == "California")
stations_sf_4269 <- st_transform(stations_sf, crs = st_crs(California))
WW_Watershed_4269 <- st_transform(WW_Watershed, crs = st_crs(California))
```
